Characterization of the microbial and fungal communities in ancient pottery from Neolithic southwestern China

### 2024-02-09 analysis/paper/paper.qmd
work on results

>>>>

At the family level, significant differences were observed between pottery exterior samples and control samples, and between pottery exterior and interior samples. *Paenibacillaceae*, *Erysipelotrichaceae*, and *Xiphinematobacteraceae* were more abundant in pottery exterior samples than those in control samples (P <0.05). In addition to *Paenibacillaceae* and *Xiphinematobacteraceae*, *Phycisphaeraceae* was more abundant in pottery exterior samples than in pottery interior samples (P <0.05).
